% Created 2022-03-30 Wed 23:06
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{theena}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={theena},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\tableofcontents

TITLE: \textbf{\textbf{Pala}} 
CREDIT: Written by
AUTHORS: Vindhya Buthpitiya, Theena Kumaragurunathan
NOTES: Working Production Draft

COPYRIGHT: (c) 2022, Vindhya Buthpitiya, Theena Kumaragurunathan


Sahodaraya


\section{Questions to Pala}
\label{sec:orge752f4d}

\subsection{Deniyaya}
\label{sec:org841187a}

\begin{itemize}
\item Had the village changed much since your childhood - socially/economically/politically?
\item How so?
\item With the war and unrest in in various parts of the island, this was a turbulent period in Sri Lanka. Did this seep into the village in any way?
\item Did you notice any significant changes to life in the village of what is happening elsewhere on the island?
\item I imagine military recruitment and its impact on villages in the rural south as well as the burgeoning unrest with the JVP, widespread poverty
\item Do you have any memories of any such specific incidents?
\end{itemize}

\subsection{Pallegama}
\label{sec:orgf9f50ab}

\subsubsection{Tell us about your time in Pallegama?}
\label{sec:orgdb69ca9}
\subsubsection{Who did you stay with?}
\label{sec:orge8612b1}
\subsubsection{How often did you go back home to your family?}
\label{sec:orgd1c8d4e}
\subsubsection{What did you study at the Pallegama school?}
\label{sec:orgb8eea26}
\subsubsection{Who were the other students there?}
\label{sec:orgaced4e3}
\subsubsection{Who taught you?}
\label{sec:org5e21090}
\subsubsection{What was the learning environment like?}
\label{sec:org8b059ea}
\subsubsection{Who were your friends with?}
\label{sec:org76f672d}
\subsubsection{What were you interested in beyond your studies?}
\label{sec:org1ff9f60}
\subsubsection{What did you do outside the time you were studying?}
\label{sec:org9d51f23}
\subsubsection{Do you have any specific memories about this time?}
\label{sec:org2a91df9}
\subsubsection{What was the wider environment in Pallegama like?}
\label{sec:orge58cf03}
\subsubsection{How was it different to the village?}
\label{sec:orgb0ec5be}
\subsubsection{How did you feel about this new environment?}
\label{sec:orgfc8ac71}
\subsubsection{The wider political context in Sri Lanka is worsening at this point in time, and is this becoming visible in your village and Pallegama?***}
\label{sec:org6ca7e3e}
\subsubsection{Did you know people who were involved in the JVP?******}
\label{sec:org410fded}
\subsubsection{How did you get to know them?***}
\label{sec:org663a0cc}
\subsubsection{What did you think of them?}
\label{sec:orga955866}
\subsubsection{What did you think of their political ideas?}
\label{sec:orgf10b172}
\subsubsection{Did these appeal to you?}
\label{sec:org27f5914}
\subsubsection{Did you feel motivated to support or contribute in some way?}
\label{sec:org9c80604}


\subsection{Trauma - Skip this section unless he changes his mind}
\label{sec:org9a0bbe2}

\subsubsection{Who helped you through that time?}
\label{sec:orgdef94c9}
\subsubsection{Did you keep making art at this time?}
\label{sec:org48f9e50}
\subsubsection{Did it help?}
\label{sec:org973a70b}
\subsubsection{How long did you stay at home?}
\label{sec:org4d21d39}
\subsubsection{When did you return to Pallegama?}
\label{sec:orgad4e93e}
\subsubsection{What was it like to return to Pallegama and your education?}
\label{sec:orgcf27bbc}
\subsubsection{It's impossible to imagine the trauma of that you underwent in that time in your life. Looking back, how do you think that experience changed/impacted you?}
\label{sec:org35154e4}
\subsubsection{Does this encounter with violence influence your work?}
\label{sec:org97fd26b}


\subsection{Colonial violence x state violence}
\label{sec:org1d5b08e}

\subsubsection{How so?}
\label{sec:org3730d18}
\subsubsection{How would you describe this period of violence in Sri Lanka?}
\label{sec:org7d25d66}
\subsubsection{Does it feature in your art?}
\label{sec:org519aec9}

\subsection{Matara}
\label{sec:org6163489}

\subsubsection{Can you tell us about your few months  in the village before you moved to Matara?}
\label{sec:orgeb7f06a}
\subsubsection{When did you leave the village?}
\label{sec:org6225d31}
\subsubsection{Why did you leave?}
\label{sec:orged39ead}

\subsection{Pala leaves to go take his Advanced Level exams in a school in Matara}
\label{sec:orga6e0e45}

\subsubsection{Did anyone in particular encourage you to leave?}
\label{sec:org3ad6e02}
\subsubsection{Had you been to Matara before?}
\label{sec:orge1fc32a}
\subsubsection{What for?}
\label{sec:org6f9d5ec}
\subsubsection{Do you remember the day you left the village?}
\label{sec:orgec8a310}
\subsubsection{Do you remember what you felt?}
\label{sec:org2a534cf}
\subsubsection{Do you remember what happened when you arrived in Matara?}
\label{sec:orge0c78f1}
\subsubsection{Do you remember wha you felt?}
\label{sec:orge602e2d}
\subsubsection{Did you travel by yourself or with someone else?}
\label{sec:org175edd6}
\subsubsection{Where did you stay?}
\label{sec:orgbe269f9}
\subsubsection{What did you do next?}
\label{sec:org4912c4b}
\subsubsection{Pala attempts to enroll at Rahula College in Matara,which requires a hefty admission fee. He refuses to burden his family with the cost and enrolls at the Pirivena next door so that he can pursue his A/L in fine art}
\label{sec:orgee9e324}

\subsubsection{What did you study at the Pirivena?}
\label{sec:org30e59fd}
\subsubsection{Who were the other students there?}
\label{sec:orgaa29ed7}
\subsubsection{Who taught you?}
\label{sec:org205753b}
\subsubsection{What was the learning environment like?}
\label{sec:org21b2685}
\subsubsection{Where were you living during this time?}
\label{sec:org989f02a}
\subsubsection{Who were your friends with?}
\label{sec:org1e46372}
\subsubsection{What were you interested in beyond your studies?}
\label{sec:org1f4b296}
\subsubsection{What did you do outside the time you were studying in the pirivena?}
\label{sec:orge2004ed}
\subsubsection{Do you have any specific memories about this time?}
\label{sec:orgb2993a1}
\subsubsection{What was the wider environment in Matara like?}
\label{sec:orgf560416}
\subsubsection{How was it different to the village?}
\label{sec:orgaff3f19}
\subsubsection{How did you feel about this new environment?}
\label{sec:org87329a5}
\subsubsection{Did you spend time with other people or did you find yourself quite isolated?}
\label{sec:org7e55310}
\subsubsection{What did you do after you finished your A/Ls?}
\label{sec:orgfca00ba}

\subsection{Signboard painting for a landsale}
\label{sec:org72a5da7}

\subsubsection{What did you want do at this point in your life?}
\label{sec:org797eb2f}
\subsubsection{Pala's brother discouraged him from his request to join him in to Galle to work in the brother's jewellery workshop and was instrumental to Pala's entrace into university}
\label{sec:org20e36a5}
\subsubsection{Tell us about your brother?}
\label{sec:org2ffb21a}
\subsubsection{What was he like?}
\label{sec:orgde1062e}
\subsubsection{What did he do?}
\label{sec:org81e50ab}
\subsubsection{What role did your borther play in your life?}
\label{sec:org364af30}
\subsubsection{Do you have any specific memories about your brother?}
\label{sec:orgdbd2550}

\section{Questions to Pala's Family}
\label{sec:org80d1560}

\subsection{SAFE QUESTIONS}
\label{sec:org11f87f7}

\subsubsection{Can you describe the time Pala left to go to school in Pallegama?}
\label{sec:org932b66e}
\subsubsection{How did you maintain contact with Pala was in Pallegama?}
\label{sec:orgd7895d5}
\subsubsection{Who was he staying with?}
\label{sec:org219554f}
\subsubsection{How often did you see him?}
\label{sec:orgc81579d}
\subsubsection{How often did he come home?}
\label{sec:orgc884f4e}

\subsection{RED FLAG QUESTIONS: WHEN PALA WAS MIA}
\label{sec:org372ec30}

\subsubsection{How did you get to know what happened to him when he was there?}
\label{sec:orgdd27365}
\subsubsection{How did you feel about this?}
\label{sec:org1f20a27}
\subsubsection{What happened after?}
\label{sec:org0adfecf}
\subsubsection{Did you look for him? How/where?}
\label{sec:org7d56c42}
\subsubsection{Did you go to the police or anywhere else?}
\label{sec:org1849c9a}
\subsubsection{How did you find out where he was?}
\label{sec:org16e0f38}
\subsubsection{What happpened next?}
\label{sec:orga64b6ac}
\subsubsection{What was it like to see him again after three months?}
\label{sec:orgca0f062}
\subsubsection{Did you take him back home?}
\label{sec:orgeb9df64}
\subsubsection{What was that time at home like?}
\label{sec:orgd99a849}
\subsubsection{This must have been an incredibly difficult time for you, did this change your relationships within the family in any way?}
\label{sec:orgf080afe}
\subsubsection{How did you recover from this experience?}
\label{sec:org7180d40}
\subsubsection{Is it possible to recover from such an experience?}
\label{sec:orgcb79911}
\subsubsection{Were you keen for Pala to leave the village after this?}
\label{sec:orgc7aa038}
\subsubsection{What happened next?}
\label{sec:org2a462a7}

\subsection{GENERIC BEESHANAYA QUESTIONS}
\label{sec:org0956372}

\subsubsection{What did you encourage Pala to do?}
\label{sec:orgdd10d86}
\subsubsection{How did this period of the beeshanaya/terror affect the village at large?}
\label{sec:org245b238}
\subsubsection{What changed in the village in its aftermath?}
\label{sec:org26f2a38}
\subsubsection{With the war and unrest in in various parts of the island, this was a turbulent period in Sri Lanka. Did this seep into the village in any way?}
\label{sec:org93ebd14}
\subsubsection{Did you notice any significant changes to life in the village of what is happening elsewhere on the island?}
\label{sec:org5508a3d}
\subsubsection{Do you have any memories of any such specific incidents?}
\label{sec:org56cbc3b}
\subsubsection{Can you describe the time Pala left the village go to school in Matara?}
\label{sec:orge17e6bc}
\subsubsection{Had he expressed a desire to leave?}
\label{sec:org4257e96}
\subsubsection{How did you feel about him leaving?}
\label{sec:org16bf2f2}
\subsubsection{Did you encourage him to leave?}
\label{sec:orga5cee26}
\subsubsection{How did you maintain contact with Pala was in Matara?}
\label{sec:orge479a53}
\subsubsection{Who was he staying with?}
\label{sec:org8d2b239}
\subsubsection{How often did you see him?}
\label{sec:org8e7d8f7}
\subsubsection{How often did he come home?}
\label{sec:orgf6581f5}
\subsubsection{What was his life in Matara like?}
\label{sec:org6f64faa}
\subsubsection{How does Pala end up going to Colombo?}
\label{sec:org14a2992}
\end{document}
